---
title: "Field Time"
author: "Joseph C. Ballenger, PhD"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: "hide"
    dev: "png"
    fig_height: 4.5
    fig_width: 6.5
    highllight: "tango"
    keep_md: TRUE
    smart: TRUE
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    df_print: "paged"
  pdf_document:
    toc: TRUE
    toc_depth: 2
    fig.width: 13.33
    fig.height: 7.5
    fig.crop: TRUE
    dev: "png"
    df_print: "tibble"
    highlight: "tango"
    keep_tex: TRUE
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# knitr options setting
knitr::opts_chunk$set(autodep = TRUE, fig.show = 'asis', fig.width = 13.33,
                      fig.height = 7.5, dev = "png", tidy = TRUE, 
                      dev.args = list(type = "windows", family = "serif"), 
                      dpi = 800, cache = TRUE, message = FALSE, echo = TRUE,
                      warning = FALSE)
# Number printing options
options(digits = 4)
# Required libraries
library(tidyverse)
library(FSA)
library(extrafont)
library(readxl)
library(survey)
```

```{r}
fig.width.powerpoint <- 13.33
fig.height.powerpoint <- 7.5
fig.width.word.l <- 6.5
fig.width.word.p <- 9
fig.height.word.l <- 3.5
fig.height.word.p <- 6

font.size.word <- 12
font.size.powerpoint <- 18
```

```{r}
Days <- 365
Weeks <- Days / 7
Weekdays <- Weeks * 5
TotalHrs <- Weekdays * 7.5
Hrs.NoHolidays <- TotalHrs - 7.5*13
Hrs.LessAL <- Hrs.NoHolidays - 7.5*15
Hrs.LessSL <- Hrs.LessAL - 7.5*15
```

```{r}
CT <- 12
BR <- 12
AB <- 10
AR <- 6
CH <- 6
LW <- 6
MB <- 8
RH <- 8
WB <- 10

CM <- 10
LE <- 8
UA <- 6
UC <- 6
EW <- 10
```

# Trammel Net
## Original
```{r}
Original.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 12
Original.Trammel.Hrs.Crew <- Original.Trammel.Hrs.Person * 6
Original.Trammel.ManYears <- Original.Trammel.Hrs.Crew / Hrs.LessSL
Original.Trammel.Days <- 2 * 4 + 7 * 12
```

## February-December; PRS Status Quo
```{r}
FebDec.PRSStatusQuo.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 11
FebDec.PRSStatusQuo.Trammel.Hrs.Crew <- FebDec.PRSStatusQuo.Trammel.Hrs.Person * 6
FebDec.PRSStatusQuo.Trammel.ManYears <- FebDec.PRSStatusQuo.Trammel.Hrs.Crew / Hrs.LessSL
FebDec.PRSStatusQuo.Trammel.Days <- 2 * 4 + 7 * 11
```

## March-December; PRS Status Quo
```{r}
MarDec.PRSStatusQuo.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 10
MarDec.PRSStatusQuo.Trammel.Hrs.Crew <- MarDec.PRSStatusQuo.Trammel.Hrs.Person * 6
MarDec.PRSStatusQuo.Trammel.ManYears <- MarDec.PRSStatusQuo.Trammel.Hrs.Crew / Hrs.LessSL
MarDec.PRSStatusQuo.Trammel.Days <- 2 * 4 + 7 * 10
```

## March-November; PRS Status Quo
```{r}
MarNov.PRSStatusQuo.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 9
MarNov.PRSStatusQuo.Trammel.Hrs.Crew <- MarNov.PRSStatusQuo.Trammel.Hrs.Person * 6
MarNov.PRSStatusQuo.Trammel.ManYears <- MarNov.PRSStatusQuo.Trammel.Hrs.Crew / Hrs.LessSL
MarNov.PRSStatusQuo.Trammel.Days <- 2 * 4 + 7 * 9
```

## 8 Months; PRS Status Quo
```{r}
Months8.PRSStatusQuo.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 8
Months8.PRSStatusQuo.Trammel.Hrs.Crew <- Months8.PRSStatusQuo.Trammel.Hrs.Person * 6
Months8.PRSStatusQuo.Trammel.ManYears <- Months8.PRSStatusQuo.Trammel.Hrs.Crew / Hrs.LessSL
Months8.PRSStatusQuo.Trammel.Days <- 2 * 4 + 7 * 8
```

## 7 Months; PRS Status Quo
```{r}
Months7.PRSStatusQuo.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 7
Months7.PRSStatusQuo.Trammel.Hrs.Crew <- Months7.PRSStatusQuo.Trammel.Hrs.Person * 6
Months7.PRSStatusQuo.Trammel.ManYears <- Months7.PRSStatusQuo.Trammel.Hrs.Crew / Hrs.LessSL
Months7.PRSStatusQuo.Trammel.Days <- 2 * 4 + 7 * 7
```

## 6 Months; PRS Status Quo
```{r}
Months6.PRSStatusQuo.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 6
Months6.PRSStatusQuo.Trammel.Hrs.Crew <- Months6.PRSStatusQuo.Trammel.Hrs.Person * 6
Months6.PRSStatusQuo.Trammel.ManYears <- Months6.PRSStatusQuo.Trammel.Hrs.Crew / Hrs.LessSL
Months6.PRSStatusQuo.Trammel.Days <- 2 * 4 + 7 * 6
```

## 5 Months; PRS Status Quo
```{r}
Months5.PRSStatusQuo.Trammel.Hrs.Person <- (CT + BR) * 4 + (AB + AR + CH + LW + MB + RH + WB) * 5
Months5.PRSStatusQuo.Trammel.Hrs.Crew <- Months5.PRSStatusQuo.Trammel.Hrs.Person * 6
Months5.PRSStatusQuo.Trammel.ManYears <- Months5.PRSStatusQuo.Trammel.Hrs.Crew / Hrs.LessSL
Months5.PRSStatusQuo.Trammel.Days <- 2 * 4 + 7 * 5
```

## Merge Strata; Monthly Sampling; 12 Months
```{r}
Months12Merge.Trammel.Hrs.Person <- (CT) * 7 + (AB + AR + CH + LW + MB + WB) * 12
Months12Merge.Trammel.Hrs.Crew <- Months12Merge.Trammel.Hrs.Person * 6
Months12Merge.Trammel.ManYears <- Months12Merge.Trammel.Hrs.Crew / Hrs.LessSL
Months12Merge.Trammel.Days <- 7 * 12
```

## Merge Strata; Monthly Sampling; 11 Months
```{r}
Months11Merge.Trammel.Hrs.Person <- (CT) * 7 + (AB + AR + CH + LW + MB + WB) * 11
Months11Merge.Trammel.Hrs.Crew <- Months11Merge.Trammel.Hrs.Person * 6
Months11Merge.Trammel.ManYears <- Months11Merge.Trammel.Hrs.Crew / Hrs.LessSL
Months11Merge.Trammel.Days <- 7 * 11
```

## Merge Strata; Monthly Sampling; 10 Months
```{r}
Months10Merge.Trammel.Hrs.Person <- (CT) * 7 + (AB + AR + CH + LW + MB + WB) * 10
Months10Merge.Trammel.Hrs.Crew <- Months10Merge.Trammel.Hrs.Person * 6
Months10Merge.Trammel.ManYears <- Months10Merge.Trammel.Hrs.Crew / Hrs.LessSL
Months10Merge.Trammel.Days <- 7 * 10
```

## Merge Strata; Monthly Sampling; 9 Months
```{r}
Months9Merge.Trammel.Hrs.Person <- (CT) * 7 + (AB + AR + CH + LW + MB + WB) * 9
Months9Merge.Trammel.Hrs.Crew <- Months9Merge.Trammel.Hrs.Person * 6
Months9Merge.Trammel.ManYears <- Months9Merge.Trammel.Hrs.Crew / Hrs.LessSL
Months9Merge.Trammel.Days <- 7 * 9
```

## Merge Strata; Monthly Sampling; 8 Months
```{r}
Months8Merge.Trammel.Hrs.Person <- (CT) * 7 + (AB + AR + CH + LW + MB + WB) * 8
Months8Merge.Trammel.Hrs.Crew <- Months8Merge.Trammel.Hrs.Person * 6
Months8Merge.Trammel.ManYears <- Months8Merge.Trammel.Hrs.Crew / Hrs.LessSL
Months8Merge.Trammel.Days <- 7 * 8
```

## Merge Strata; Monthly Sampling; 7 Months
```{r}
Months7Merge.Trammel.Hrs.Person <- (CT) * 7 + (AB + AR + CH + LW + MB + WB) * 7
Months7Merge.Trammel.Hrs.Crew <- Months7Merge.Trammel.Hrs.Person * 6
Months7Merge.Trammel.ManYears <- Months7Merge.Trammel.Hrs.Crew / Hrs.LessSL
Months7Merge.Trammel.Days <- 7 * 7
```

## Merge Strata; Monthly Sampling; 6 Months
```{r}
Months6Merge.Trammel.Hrs.Person <- (CT) * 7 + (AB + AR + CH + LW + MB + WB) * 6
Months6Merge.Trammel.Hrs.Crew <- Months6Merge.Trammel.Hrs.Person * 6
Months6Merge.Trammel.ManYears <- Months6Merge.Trammel.Hrs.Crew / Hrs.LessSL
Months6Merge.Trammel.Days <- 7 * 6
```

# Electrofishing
## Original
```{r}
Original.Electro.Hrs.Person <- (CM + LE + UA + UC + EW) * 12
Original.Electro.Hrs.Crew <- Original.Electro.Hrs.Person * 3
Original.Electro.ManYears <- Original.Electro.Hrs.Crew / Hrs.LessSL
Original.Electro.Days <- 5 * 12
```

## Months 11
```{r}
Months11.Electro.Hrs.Person <- (CM + LE + UA + UC + EW) * 11
Months11.Electro.Hrs.Crew <- Months11.Electro.Hrs.Person * 3
Months11.Electro.ManYears <- Months11.Electro.Hrs.Crew / Hrs.LessSL
Months11.Electro.Days <- 5 * 11
```

## Months 10
```{r}
Months10.Electro.Hrs.Person <- (CM + LE + UA + UC + EW) * 10
Months10.Electro.Hrs.Crew <- Months10.Electro.Hrs.Person * 3
Months10.Electro.ManYears <- Months10.Electro.Hrs.Crew / Hrs.LessSL
Months10.Electro.Days <- 5 * 10
```

## Months 9
```{r}
Months9.Electro.Hrs.Person <- (CM + LE + UA + UC + EW) * 9
Months9.Electro.Hrs.Crew <- Months9.Electro.Hrs.Person * 3
Months9.Electro.ManYears <- Months9.Electro.Hrs.Crew / Hrs.LessSL
Months9.Electro.Days <- 5 * 9
```

## Months 8
```{r}
Months8.Electro.Hrs.Person <- (CM + LE + UA + UC + EW) * 8
Months8.Electro.Hrs.Crew <- Months8.Electro.Hrs.Person * 3
Months8.Electro.ManYears <- Months8.Electro.Hrs.Crew / Hrs.LessSL
Months8.Electro.Days <- 5 * 8
```

## Months 7
```{r}
Months7.Electro.Hrs.Person <- (CM + LE + UA + UC + EW) * 7
Months7.Electro.Hrs.Crew <- Months7.Electro.Hrs.Person * 3
Months7.Electro.ManYears <- Months7.Electro.Hrs.Crew / Hrs.LessSL
Months7.Electro.Days <- 5 * 7
```

## Months 6
```{r}
öMonths6.Electro.Hrs.Person <- (CM + LE + UA + UC + EW) * 6
Months6.Electro.Hrs.Crew <- Months6.Electro.Hrs.Person * 3
Months6.Electro.ManYears <- Months6.Electro.Hrs.Crew / Hrs.LessSL
Months6.Electro.Days <- 5 * 6
```

