---
title: 'Survey Change Investigation'
author: "Joseph C. Ballenger, PhD"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: "hide"
    dev: "png"
    fig_height: 4.5
    fig_width: 6.5
    highllight: "tango"
    keep_md: TRUE
    smart: TRUE
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    df_print: "paged"
  pdf_document:
    toc: TRUE
    toc_depth: 2
    fig.width: 13.33
    fig.height: 7.5
    fig.crop: TRUE
    dev: "png"
    df_print: "tibble"
    highlight: "tango"
    keep_tex: TRUE
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# knitr options setting
knitr::opts_chunk$set(autodep = TRUE, fig.show = 'asis', fig.width = 13.33,
                      fig.height = 7.5, dev = "png", tidy = TRUE, 
                      dev.args = list(type = "windows", family = "serif"), 
                      dpi = 800, cache = TRUE, message = FALSE, echo = TRUE,
                      warning = FALSE)
# Number printing options
options(digits = 4)
# Required libraries
library(tidyverse)
library(FSA)
library(extrafont)
library(readxl)
library(survey)
```

```{r}
fig.width.powerpoint <- 13.33
fig.height.powerpoint <- 7.5
fig.width.word.l <- 6.5
fig.width.word.p <- 9
fig.height.word.l <- 3.5
fig.height.word.p <- 6

font.size.word <- 12
font.size.powerpoint <- 18
```

# Data Sets
## Trammel
```{r}
setwd("D:/Estuarine Finfish Research/Survey-Redesign/Trammel Net")
Trammel.Original <- read.csv("Annual CPUE by Species - Original.csv")
Trammel.All.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 6 months.csv")
Trammel.All.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 7 months.csv")
Trammel.All.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 8 months.csv")
Trammel.All.9 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 9 months.csv")
Trammel.All.10 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 10 months.csv")
Trammel.All.11 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 11 months.csv")
Trammel.FebDec <- read.csv("Annual CPUE by Species - Sub-Setting Sampling to February - December.csv")
Trammel.FebDec.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 6 months per year.csv")
Trammel.FebDec.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 7 months per year.csv")
Trammel.FebDec.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 8 months per year.csv")
Trammel.FebDec.9 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 9 months per year.csv")
Trammel.FebDec.10 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 10 months per year.csv")
Trammel.MarDec <- read.csv("Annual CPUE by Species - Sub-Setting Sampling to March - December.csv")
Trammel.MarDec.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 6 months per year.csv")
Trammel.MarDec.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 7 months per year.csv")
Trammel.MarDec.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 8 months per year.csv")
Trammel.MarDec.9 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 9 months per year.csv")
Trammel.MarNov <- read.csv("Annual CPUE by Species - Sub-Setting Sampling to March - November.csv")
Trammel.MarNov.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - November and 6 months per year.csv")
Trammel.MarNov.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - November and 7 months per year.csv")
Trammel.MarNov.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - November and 8 months per year.csv")
```

## Electrofishing
```{r}
setwd("D:/Estuarine Finfish Research/Survey-Redesign/Electrofishing")
Electro.Original <- read.csv("Annual CPUE by Species - Original - Electrofishing.csv")
Electro.All.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 6 months - Electrofishing.csv")
Electro.All.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 7 months - Electrofishing.csv")
Electro.All.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 8 months - Electrofishing.csv")
Electro.All.9 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 9 months - Electrofishing.csv")
Electro.All.10 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 10 months - Electrofishing.csv")
Electro.All.11 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to 11 months - Electrofishing.csv")
Electro.FebDec <- read.csv("Annual CPUE by Species - Sub-Setting Sampling to February - December - Electrofishing.csv")
Electro.FebDec.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 6 months per year - Electrofishing.csv")
Electro.FebDec.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 7 months per year - Electrofishing.csv")
Electro.FebDec.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 8 months per year - Electrofishing.csv")
Electro.FebDec.9 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 9 months per year - Electrofishing.csv")
Electro.FebDec.10 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to February - December and 10 months per year - Electrofishing.csv")
Electro.MarDec <- read.csv("Annual CPUE by Species - Sub-Setting Sampling to March - December - Electrofishing.csv")
Electro.MarDec.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 6 months per year - Electrofishing.csv")
Electro.MarDec.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 7 months per year - Electrofishing.csv")
Electro.MarDec.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 8 months per year - Electrofishing.csv")
Electro.MarDec.9 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - December and 9 months per year - Electrofishing.csv")
Electro.MarNov <- read.csv("Annual CPUE by Species - Sub-Setting Sampling to March - November - Electrofishing.csv")
Electro.MarNov.6 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - November and 6 months per year - Electrofishing.csv")
Electro.MarNov.7 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - November and 7 months per year - Electrofishing.csv")
Electro.MarNov.8 <- read.csv("Annual CPUE by Species - 1000 iterations of Sub-Setting Sampling to March - November and 8 months per year - Electrofishing.csv")
```

# CPUE Summaries
## Trammel Net
### Original
```{r}
Trammel.Summary.Org <- Trammel.Original %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.Org, "Trammel Net/CV Summaries by Species/Original.csv", 
          row.names = FALSE)
```

### All Months
#### 11 months of Sampling
```{r}
Trammel.Summary.All.11.Year <- Trammel.All.11 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.All.11.Year,
          "Trammel Net/CV Summaries by Species and Year/Sub-Setting Sampling to 11 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.All.11 <- Trammel.All.11 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.All.11,
          "Trammel Net/CV Summaries by Species/Sub-Setting Sampling to 11 months.csv", 
          row.names = FALSE)
```

#### 10 months of Sampling
```{r}
Trammel.Summary.All.10.Year <- Trammel.All.10 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.All.10.Year,
          "Trammel Net/CV Summaries by Species and Year/Sub-Setting Sampling to 10 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.All.10 <- Trammel.All.10 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.All.10,
          "Trammel Net/CV Summaries by Species/Sub-Setting Sampling to 10 months.csv", 
          row.names = FALSE)
```

#### 9 months of Sampling
```{r}
Trammel.Summary.All.9.Year <- Trammel.All.9 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.All.9.Year,
          "Trammel Net/CV Summaries by Species and Year/Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.All.9 <- Trammel.All.9 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.All.9,
          "Trammel Net/CV Summaries by Species/Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Trammel.Summary.All.8.Year <- Trammel.All.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.All.8.Year,
          "Trammel Net/CV Summaries by Species and Year/Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.All.8 <- Trammel.All.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.All.8,
          "Trammel Net/CV Summaries by Species/Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Trammel.Summary.All.7.Year <- Trammel.All.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.All.9.Year,
          "Trammel Net/CV Summaries by Species and Year/Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.All.7 <- Trammel.All.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.All.7,
          "Trammel Net/CV Summaries by Species/Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Trammel.Summary.All.6.Year <- Trammel.All.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.All.6.Year,
          "Trammel Net/CV Summaries by Species and Year/Sub-Setting Sampling to 6 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.All.6 <- Trammel.All.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.All.6,
          "Trammel Net/CV Summaries by Species/Sub-Setting Sampling to 6 months.csv", 
          row.names = FALSE)
```

### February-December Sampling
#### All Months
```{r}
Trammel.Summary.FebDec.Year <- Trammel.FebDec %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.FebDec.Year,
          "Trammel Net/CV Summaries by Species and Year/February - December Sampling.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.FebDec <- Trammel.FebDec %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.FebDec,
          "Trammel Net/CV Summaries by Species/February - December.csv", 
          row.names = FALSE)
```

#### 10 months of Sampling
```{r}
Trammel.Summary.FebDec.10.Year <- Trammel.FebDec.10 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.FebDec.10.Year,
          "Trammel Net/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 10 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.FebDec.10 <- Trammel.FebDec.10 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.FebDec.10,
          "Trammel Net/CV Summaries by Species/February - December - Sub-Setting Sampling to 10 months.csv", 
          row.names = FALSE)
```

#### 9 months of Sampling
```{r}
Trammel.Summary.FebDec.9.Year <- Trammel.FebDec.9 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.FebDec.9.Year,
          "Trammel Net/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.FebDec.9 <- Trammel.FebDec.9 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.FebDec.9,
          "Trammel Net/CV Summaries by Species/February - December - Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Trammel.Summary.FebDec.8.Year <- Trammel.FebDec.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.FebDec.8.Year,
          "Trammel Net/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.FebDec.8 <- Trammel.FebDec.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.FebDec.8,
          "Trammel Net/CV Summaries by Species/February - December - Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Trammel.Summary.FebDec.7.Year <- Trammel.FebDec.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.FebDec.7.Year,
          "Trammel Net/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.FebDec.7 <- Trammel.FebDec.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.FebDec.7,
          "Trammel Net/CV Summaries by Species/February - December - Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Trammel.Summary.FebDec.6.Year <- Trammel.FebDec.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.FebDec.6.Year,
          "Trammel Net/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 6 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.FebDec.6 <- Trammel.FebDec.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.FebDec.6,
          "Trammel Net/CV Summaries by Species/February - December - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

### March-December Sampling
#### All Months
```{r}
Trammel.Summary.MarDec.Year <- Trammel.MarDec %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarDec.Year,
          "Trammel Net/CV Summaries by Species and Year/March - December Sampling.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarDec <- Trammel.MarDec %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarDec,
          "Trammel Net/CV Summaries by Species/March - December.csv", row.names = FALSE)
```

#### 9 months of Sampling
```{r}
Trammel.Summary.MarDec.9.Year <- Trammel.MarDec.9 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarDec.9.Year,
          "Trammel Net/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarDec.9 <- Trammel.MarDec.9 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarDec.9,
          "Trammel Net/CV Summaries by Species/March - December - Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Trammel.Summary.MarDec.8.Year <- Trammel.MarDec.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarDec.8.Year,
          "Trammel Net/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarDec.8 <- Trammel.MarDec.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarDec.8,
          "Trammel Net/CV Summaries by Species/March - December - Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Trammel.Summary.MarDec.7.Year <- Trammel.MarDec.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarDec.7.Year,
          "Trammel Net/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarDec.7 <- Trammel.MarDec.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarDec.7,
          "Trammel Net/CV Summaries by Species/March - December - Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Trammel.Summary.MarDec.6.Year <- Trammel.MarDec.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarDec.6.Year,
          "Trammel Net/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 6 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarDec.6 <- Trammel.MarDec.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarDec.6,
          "Trammel Net/CV Summaries by Species/March - December - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

### March-November Sampling
#### All Months
```{r}
Trammel.Summary.MarNov.Year <- Trammel.MarNov %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarNov.Year,
          "Trammel Net/CV Summaries by Species and Year/March - November Sampling.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarNov <- Trammel.MarNov %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarNov,
          "Trammel Net/CV Summaries by Species/March - November.csv", row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Trammel.Summary.MarNov.8.Year <- Trammel.MarNov.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarNov.8.Year,
          "Trammel Net/CV Summaries by Species and Year/March - November - Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarNov.8 <- Trammel.MarNov.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarNov.8,
          "Trammel Net/CV Summaries by Species/March - November - Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Trammel.Summary.MarNov.7.Year <- Trammel.MarNov.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarNov.7.Year,
          "Trammel Net/CV Summaries by Species and Year/March - November - Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarNov.7 <- Trammel.MarNov.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarNov.7,
          "Trammel Net/CV Summaries by Species/March - November - Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Trammel.Summary.MarNov.6.Year <- Trammel.MarNov.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Trammel.Summary.MarNov.6.Year,
          "Trammel Net/CV Summaries by Species and Year/March - November - Sub-Setting Sampling to 6 months.csv",
          row.names = FALSE)
```

```{r}
Trammel.Summary.MarNov.6 <- Trammel.MarNov.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Trammel.Summary.MarNov.6,
          "Trammel Net/CV Summaries by Species/March - November - Sub-Setting Sampling to 6 months.csv",
          row.names = FALSE)
```

## Electrofishing
### Original
```{r}
Electro.Summary.Org <- Electro.Original %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.Org, 
          "Electrofishing/CV Summaries by Species/Original.csv", 
          row.names = FALSE)
```

### All Months
#### 11 months of Sampling
```{r}
Electro.Summary.All.11.Year <- Electro.All.11 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.All.11.Year,
          "Electrofishing/CV Summaries by Species and Year/Sub-Setting Sampling to 11 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.All.11 <- Electro.All.11 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.All.11,
          "Electrofishing/CV Summaries by Species/Sub-Setting Sampling to 11 months.csv", row.names = FALSE)
```

#### 10 months of Sampling
```{r}
Electro.Summary.All.10.Year <- Electro.All.10 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.All.10.Year,
          "Electrofishing/CV Summaries by Species and Year/Sub-Setting Sampling to 10 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.All.10 <- Electro.All.10 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.All.10,
          "Electrofishing/CV Summaries by Species/Sub-Setting Sampling to 10 months.csv", row.names = FALSE)
```

#### 9 months of Sampling
```{r}
Electro.Summary.All.9.Year <- Electro.All.9 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.All.9.Year,
          "Electrofishing/CV Summaries by Species and Year/Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

```{r}
Electro.Summary.All.9 <- Electro.All.9 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.All.9,
          "Electrofishing/CV Summaries by Species/Sub-Setting Sampling to 9 months.csv", 
          row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Electro.Summary.All.8.Year <- Electro.All.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.All.8.Year,
          "Electrofishing/CV Summaries by Species and Year/Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

```{r}
Electro.Summary.All.8 <- Electro.All.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.All.8,
          "Electrofishing/CV Summaries by Species/Sub-Setting Sampling to 8 months.csv", 
          row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Electro.Summary.All.7.Year <- Electro.All.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.All.7.Year,
          "Electrofishing/CV Summaries by Species and Year/Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

```{r}
Electro.Summary.All.7 <- Electro.All.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.All.7,
          "Electrofishing/CV Summaries by Species/Sub-Setting Sampling to 7 months.csv", 
          row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Electro.Summary.All.6.Year <- Electro.All.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.All.6.Year,
          "Electrofishing/CV Summaries by Species and Year/Sub-Setting Sampling to 6 months.csv", 
          row.names = FALSE)
```

```{r}
Electro.Summary.All.6 <- Electro.All.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.All.6,
          "Electrofishing/CV Summaries by Species/Sub-Setting Sampling to 6 months.csv", 
          row.names = FALSE)
```

### February-December Sampling
#### All Months
```{r}
Electro.Summary.FebDec.Year <- Electro.FebDec %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.FebDec.Year,
          "Electrofishing/CV Summaries by Species and Year/February - December Sampling.csv", row.names = FALSE)
```

```{r}
Electro.Summary.FebDec <- Electro.FebDec %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.FebDec,
          "Electrofishing/CV Summaries by Species/February - December.csv", row.names = FALSE)
```

#### 10 months of Sampling
```{r}
Electro.Summary.FebDec.10.Year <- Electro.FebDec.10 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.FebDec.10.Year,
          "Electrofishing/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 10 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.FebDec.10 <- Electro.FebDec.10 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.FebDec.10,
          "Electrofishing/CV Summaries by Species/February - December - Sub-Setting Sampling to 10 months.csv", row.names = FALSE)
```

#### 9 months of Sampling
```{r}
Electro.Summary.FebDec.9.Year <- Electro.FebDec.9 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.FebDec.9.Year,
          "Electrofishing/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 9 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.FebDec.9 <- Electro.FebDec.9 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.FebDec.9,
          "Electrofishing/CV Summaries by Species/February - December - Sub-Setting Sampling to 9 months.csv", row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Electro.Summary.FebDec.8.Year <- Electro.FebDec.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.FebDec.8.Year,
          "Electrofishing/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 8 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.FebDec.8 <- Electro.FebDec.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.FebDec.8,
          "Electrofishing/CV Summaries by Species/February - December - Sub-Setting Sampling to 8 months.csv", row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Electro.Summary.FebDec.7.Year <- Electro.FebDec.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.FebDec.7.Year,
          "Electrofishing/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 7 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.FebDec.7 <- Electro.FebDec.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.FebDec.7,
          "Electrofishing/CV Summaries by Species/February - December - Sub-Setting Sampling to 7 months.csv", row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Electro.Summary.FebDec.6.Year <- Electro.FebDec.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.FebDec.6.Year,
          "Electrofishing/CV Summaries by Species and Year/February - December - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.FebDec.6 <- Electro.FebDec.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.FebDec.6,
          "Electrofishing/CV Summaries by Species/February - December - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

### March-December Sampling
#### All Months
```{r}
Electro.Summary.MarDec.Year <- Electro.MarDec %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarDec.Year,
          "Electrofishing/CV Summaries by Species and Year/March - December Sampling.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarDec <- Electro.MarDec %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarDec,
          "Electrofishing/CV Summaries by Species/March - December.csv", row.names = FALSE)
```

#### 9 months of Sampling
```{r}
Electro.Summary.MarDec.9.Year <- Electro.MarDec.9 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarDec.9.Year,
          "Electrofishing/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 9 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarDec.9 <- Electro.MarDec.9 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarDec.9,
          "Electrofishing/CV Summaries by Species/March - December - Sub-Setting Sampling to 9 months.csv", row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Electro.Summary.MarDec.8.Year <- Electro.MarDec.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarDec.8.Year,
          "Electrofishing/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 8 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarDec.8 <- Electro.MarDec.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarDec.8,
          "Electrofishing/CV Summaries by Species/March - December - Sub-Setting Sampling to 8 months.csv", row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Electro.Summary.MarDec.7.Year <- Electro.MarDec.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarDec.7.Year,
          "Electrofishing/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 7 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarDec.7 <- Electro.MarDec.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarDec.7,
          "Electrofishing/CV Summaries by Species/March - December - Sub-Setting Sampling to 7 months.csv", row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Electro.Summary.MarDec.6.Year <- Electro.MarDec.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarDec.6.Year,
          "Electrofishing/CV Summaries by Species and Year/March - December - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarDec.6 <- Electro.MarDec.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarDec.6,
          "Electrofishing/CV Summaries by Species/March - December - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

### March-November Sampling
#### All Months
```{r}
Electro.Summary.MarNov.Year <- Electro.MarNov %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarNov.Year,
          "Electrofishing/CV Summaries by Species and Year/March - November Sampling.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarNov <- Electro.MarNov %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarNov,
          "Electrofishing/CV Summaries by Species/March - November.csv", row.names = FALSE)
```

#### 8 months of Sampling
```{r}
Electro.Summary.MarNov.8.Year <- Electro.MarNov.8 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarNov.8.Year,
          "Electrofishing/CV Summaries by Species and Year/March - November - Sub-Setting Sampling to 8 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarNov.8 <- Electro.MarNov.8 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarNov.8,
          "Electrofishing/CV Summaries by Species/March - November - Sub-Setting Sampling to 8 months.csv", row.names = FALSE)
```

#### 7 months of Sampling
```{r}
Electro.Summary.MarNov.7.Year <- Electro.MarNov.7 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarNov.7.Year,
          "Electrofishing/CV Summaries by Species and Year/March - November - Sub-Setting Sampling to 7 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarNov.7 <- Electro.MarNov.7 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarNov.7,
          "Electrofishing/CV Summaries by Species/March - November - Sub-Setting Sampling to 7 months.csv", row.names = FALSE)
```

#### 6 months of Sampling
```{r}
Electro.Summary.MarNov.6.Year <- Electro.MarNov.6 %>%
  group_by(Year, Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV))
write.csv(Electro.Summary.MarNov.6.Year,
          "Electrofishing/CV Summaries by Species and Year/March - November - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

```{r}
Electro.Summary.MarNov.6 <- Electro.MarNov.6 %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV)
write.csv(Electro.Summary.MarNov.6,
          "Electrofishing/CV Summaries by Species/March - November - Sub-Setting Sampling to 6 months.csv", row.names = FALSE)
```

# Combined Data Sets
## Trammel
### Originals
```{r}
Trammel.Original <- Trammel.Original %>%
  mutate(Run = 1, 
         Months = "Jan-Dec",
         `Sub-Sampling` = "12 Months")
Trammel.All.11 <- Trammel.All.11 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "11 Months")
Trammel.All.10 <- Trammel.All.10 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "10 Months")
Trammel.All.9 <- Trammel.All.9 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "9 Months")
Trammel.All.8 <- Trammel.All.8 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "8 Months")
Trammel.All.7 <- Trammel.All.7 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "7 Months")
Trammel.All.6 <- Trammel.All.6 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "6 Months")
Trammel.FebDec <- Trammel.FebDec %>%
  mutate(Run = 1,
         Months = "Feb-Dec",
         `Sub-Sampling` = "11 Months")
Trammel.FebDec.10 <- Trammel.FebDec.10 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "10 Months")
Trammel.FebDec.9 <- Trammel.FebDec.9 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "9 Months")
Trammel.FebDec.8 <- Trammel.FebDec.8 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "8 Months")
Trammel.FebDec.7 <- Trammel.FebDec.7 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "7 Months")
Trammel.FebDec.6 <- Trammel.FebDec.6 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "6 Months")
Trammel.MarDec <- Trammel.MarDec %>%
  mutate(Run = 1,
         Months = "Mar-Dec",
         `Sub-Sampling` = "10 Months")
Trammel.MarDec.9 <- Trammel.MarDec.9 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "9 Months")
Trammel.MarDec.8 <- Trammel.MarDec.8 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "8 Months")
Trammel.MarDec.7 <- Trammel.MarDec.7 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "7 Months")
Trammel.MarDec.6 <- Trammel.FebDec.6 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "6 Months")
Trammel.MarNov <- Trammel.MarNov %>%
  mutate(Run = 1, 
         Months = "Mar-Nov",
         `Sub-Sampling` = "9 Months")
Trammel.MarNov.8 <- Trammel.MarNov.8 %>%
  mutate(Months = "Mar-Nov",
         `Sub-Sampling` = "8 Months")
Trammel.MarNov.7 <- Trammel.MarNov.7 %>%
  mutate(Months = "Mar-Nov",
         `Sub-Sampling` = "7 Months")
Trammel.MarNov.6 <- Trammel.MarNov.6 %>%
  mutate(Months = "Mar-Nov",
         `Sub-Sampling` = "6 Months")
```

### Combined
```{r}
Trammel.Combined <- rbind(Trammel.Original, Trammel.All.11, Trammel.All.10, Trammel.All.9,
                          Trammel.All.8, Trammel.All.7, Trammel.All.6, Trammel.FebDec,
                          Trammel.FebDec.10, Trammel.FebDec.9, Trammel.FebDec.8,
                          Trammel.FebDec.7, Trammel.FebDec.6, Trammel.MarDec, Trammel.MarDec.9,
                          Trammel.MarDec.8, Trammel.MarDec.7, Trammel.MarDec.6, Trammel.MarNov,
                          Trammel.MarNov.8, Trammel.MarNov.7, Trammel.MarNov.6) %>%
mutate(Months = factor(Months,
                       levels = c("Jan-Dec", "Feb-Dec", "Mar-Dec", "Mar-Nov")),
       `Sub-Sampling` = factor(`Sub-Sampling`,
                               levels = c("12 Months", "11 Months", "10 Months", "9 Months",
                                          "8 Months", "7 Months", "6 Months")),
       Month.SubSample = factor(paste(Months, `Sub-Sampling`, sep = "\n"),
                                levels = c("Jan-Dec\n12 Months","Jan-Dec\n11 Months",
                                           "Jan-Dec\n10 Months", "Jan-Dec\n9 Months",
                                           "Jan-Dec\n8 Months", "Jan-Dec\n7 Months",
                                           "Jan-Dec\n6 Months","Feb-Dec\n11 Months",
                                           "Feb-Dec\n10 Months", "Feb-Dec\n9 Months",
                                           "Feb-Dec\n8 Months", "Feb-Dec\n7 Months",
                                           "Feb-Dec\n6 Months", "Mar-Dec\n10 Months",
                                           "Mar-Dec\n9 Months", "Mar-Dec\n8 Months",
                                           "Mar-Dec\n7 Months", "Mar-Dec\n6 Months",
                                           "Mar-Nov\n9 Months", "Mar-Nov\n8 Months",
                                           "Mar-Nov\n7 Months", "Mar-Nov\n6 Months")))
write.csv(Trammel.Combined, "Trammel Net/Annual CPUE by Species.csv", row.names = FALSE)
```

### CV Statistics by Year, Species, Months Sampled, and Sampling Intensity
```{r}
Trammel.Summary.Year <- Trammel.Combined %>%
  group_by(Year, Species, Months, `Sub-Sampling`, Month.SubSample) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  ungroup()
write.csv(Trammel.Summary.Year,
          "Trammel Net/CV Summary by Year, Species, Sampling Months, and Intensity/CV Summary.csv", 
          row.names = FALSE)
```

### CV Statistics by Species, Months Sampled, and Sampling Intensity
```{r}
Trammel.Summary <- Trammel.Combined %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species, Months, `Sub-Sampling`, Month.SubSample) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV) %>%
  ungroup() %>%
  group_by(Species) %>%
  mutate(Relative.CV = (Median.CV / first(Median.CV) - 1) * 100) %>%
  arrange(Species, Median.CV) %>%
  ungroup()
write.csv(Trammel.Summary,
          "Trammel Net/CV Summary by Species, Sampling Months, and Intensity/CV Summary.csv", 
          row.names = FALSE)
```

### CPUE by Year, Species, Months Sampled, and Sampling Intensity
```{r}
Trammel.CPUE <- Trammel.Combined %>%
  group_by(Year, Species, Months, `Sub-Sampling`, Month.SubSample) %>%
  summarize(Abundance = median(Abundance),
            ci_l = median(ci_l),
            ci_u = median(ci_u)) %>%
  ungroup() 
write.csv(Trammel.CPUE,
          "Trammel Net/CPUE/Relative Abundance by Species, Sampling Months, and Intensity.csv", row.names = FALSE)
```

## Electrofishing
### Originals
```{r}
Electro.Original <- Electro.Original %>%
  mutate(Run = 1, 
         Months = "Jan-Dec",
         `Sub-Sampling` = "12 Months") %>%
  rename(Abundance = CPUE)
Electro.All.11 <- Electro.All.11 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "11 Months")
Electro.All.10 <- Electro.All.10 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "10 Months")
Electro.All.9 <- Electro.All.9 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "9 Months")
Electro.All.8 <- Electro.All.8 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "8 Months")
Electro.All.7 <- Electro.All.7 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "7 Months")
Electro.All.6 <- Electro.All.6 %>%
  mutate(Months = "Jan-Dec",
         `Sub-Sampling` = "6 Months")
Electro.FebDec <- Electro.FebDec %>%
  mutate(Run = 1,
         Months = "Feb-Dec",
         `Sub-Sampling` = "11 Months")
Electro.FebDec.10 <- Electro.FebDec.10 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "10 Months")
Electro.FebDec.9 <- Electro.FebDec.9 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "9 Months")
Electro.FebDec.8 <- Electro.FebDec.8 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "8 Months")
Electro.FebDec.7 <- Electro.FebDec.7 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "7 Months")
Electro.FebDec.6 <- Electro.FebDec.6 %>%
  mutate(Months = "Feb-Dec",
         `Sub-Sampling` = "6 Months")
Electro.MarDec <- Electro.MarDec %>%
  mutate(Run = 1,
         Months = "Mar-Dec",
         `Sub-Sampling` = "10 Months")
Electro.MarDec.9 <- Electro.MarDec.9 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "9 Months")
Electro.MarDec.8 <- Electro.MarDec.8 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "8 Months")
Electro.MarDec.7 <- Electro.MarDec.7 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "7 Months")
Electro.MarDec.6 <- Electro.FebDec.6 %>%
  mutate(Months = "Mar-Dec",
         `Sub-Sampling` = "6 Months")
Electro.MarNov <- Electro.MarNov %>%
  mutate(Run = 1,
         Months = "Mar-Nov",
         `Sub-Sampling` = "9 Months")
Electro.MarNov.8 <- Electro.MarNov.8 %>%
  mutate(Months = "Mar-Nov",
         `Sub-Sampling` = "8 Months")
Electro.MarNov.7 <- Electro.MarNov.7 %>%
  mutate(Months = "Mar-Nov",
         `Sub-Sampling` = "7 Months")
Electro.MarNov.6 <- Electro.MarNov.6 %>%
  mutate(Months = "Mar-Nov",
         `Sub-Sampling` = "6 Months")
```

### Combined
```{r}
Electro.Combined <- rbind(Electro.Original, Electro.All.11, Electro.All.10, Electro.All.9,
                          Electro.All.8, Electro.All.7, Electro.All.6, Electro.FebDec,
                          Electro.FebDec.10, Electro.FebDec.9, Electro.FebDec.8,
                          Electro.FebDec.7, Electro.FebDec.6, Electro.MarDec, Electro.MarDec.9,
                          Electro.MarDec.8, Electro.MarDec.7, Electro.MarDec.6, Electro.MarNov,
                          Electro.MarNov.8, Electro.MarNov.7, Electro.MarNov.6) %>%
mutate(Months = factor(Months,
                       levels = c("Jan-Dec", "Feb-Dec", "Mar-Dec", "Mar-Nov")),
       `Sub-Sampling` = factor(`Sub-Sampling`,
                               levels = c("12 Months", "11 Months", "10 Months", "9 Months",
                                          "8 Months", "7 Months", "6 Months")),
       Month.SubSample = factor(paste(Months, `Sub-Sampling`, sep = "\n"),
                                levels = c("Jan-Dec\n12 Months","Jan-Dec\n11 Months",
                                           "Jan-Dec\n10 Months", "Jan-Dec\n9 Months",
                                           "Jan-Dec\n8 Months", "Jan-Dec\n7 Months",
                                           "Jan-Dec\n6 Months","Feb-Dec\n11 Months",
                                           "Feb-Dec\n10 Months", "Feb-Dec\n9 Months",
                                           "Feb-Dec\n8 Months", "Feb-Dec\n7 Months",
                                           "Feb-Dec\n6 Months", "Mar-Dec\n10 Months",
                                           "Mar-Dec\n9 Months", "Mar-Dec\n8 Months",
                                           "Mar-Dec\n7 Months", "Mar-Dec\n6 Months",
                                           "Mar-Nov\n9 Months", "Mar-Nov\n8 Months",
                                           "Mar-Nov\n7 Months", "Mar-Nov\n6 Months")))
write.csv(Electro.Combined, "Electrofishing/Annual CPUE by Species.csv", row.names = FALSE)
```

### CV Statistics by Year, Species, Months Sampled, and Sampling Intensity
```{r}
Electro.Summary.Year <- Electro.Combined %>%
  group_by(Year, Species, Months, `Sub-Sampling`, Month.SubSample) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  ungroup()
write.csv(Electro.Summary.Year,
          "Electrofishing/CV Summary by Year, Species, Sampling Months, and Intensity/CV Summary.csv", row.names = FALSE)
```

### CV Statistics by Species, Months Sampled, and Sampling Intensity
```{r}
Electro.Summary <- Electro.Combined %>%
  filter(Year %in% c(2003:2018)) %>%
  group_by(Species, Months, `Sub-Sampling`, Month.SubSample) %>%
  summarize(n = sum(!is.na(cv)),
            Median.CV = median(cv, na.rm = TRUE),
            Min = min(cv, na.rm = TRUE),
            Lower = quantile(cv, 0.025, na.rm = TRUE),
            Avg.CV = mean(cv, na.rm = TRUE),
            Upper = quantile(cv, 0.0975, na.rm = TRUE),
            Max = max(cv, na.rm = TRUE)) %>%
  filter(!is.na(Avg.CV)) %>%
  arrange(Median.CV) %>%
  ungroup() %>%
  group_by(Species) %>%
  mutate(Relative.CV = (Median.CV / first(Median.CV) - 1) * 100) %>%
  arrange(Species, Median.CV) %>%
  ungroup()
write.csv(Electro.Summary,
          "Electrofishing/CV Summary by Species, Sampling Months, and Intensity/CV Summary.csv", 
          row.names = FALSE)
```

### CPUE by Year, Species, Months Sampled, and Sampling Intensity
```{r}
Electro.CPUE <- Electro.Combined %>%
  group_by(Year, Species, Months, `Sub-Sampling`, Month.SubSample) %>%
  summarize(Abundance = median(Abundance),
            ci_l = median(ci_l),
            ci_u = median(ci_u)) %>%
  ungroup() 
write.csv(Electro.CPUE,
          "Electrofishing/CPUE/Relative Abundance by Species, Sampling Months, and Intensity.csv", row.names = FALSE)
```

# Workspace Cleanup
```{r}
rm(Trammel.Original, Trammel.All.11, Trammel.All.10, Trammel.All.9, Trammel.All.8, 
   Trammel.All.7, Trammel.All.6, Trammel.FebDec, Trammel.FebDec.10, Trammel.FebDec.9, 
   Trammel.FebDec.8, Trammel.FebDec.7, Trammel.FebDec.6, Trammel.MarDec, Trammel.MarDec.9,
   Trammel.MarDec.8, Trammel.MarDec.7, Trammel.MarDec.6, Trammel.MarNov, Trammel.MarNov.8,
   Trammel.MarNov.7, Trammel.MarNov.6, Electro.Original, Electro.All.11, Electro.All.10, 
   Electro.All.9, Electro.All.8, Electro.All.7, Electro.All.6, Electro.FebDec, 
   Electro.FebDec.10, Electro.FebDec.9, Electro.FebDec.8, Electro.FebDec.7, Electro.FebDec.6, 
   Electro.MarDec, Electro.MarDec.9, Electro.MarDec.8, Electro.MarDec.7, Electro.MarDec.6, 
   Electro.MarNov, Electro.MarNov.8, Electro.MarNov.7, Electro.MarNov.6, 
   Trammel.Summary.All.11.Year, Trammel.Summary.All.10.Year, Trammel.Summary.All.9.Year, 
   Trammel.Summary.All.8.Year, Trammel.Summary.All.7.Year, Trammel.Summary.All.6.Year,
   Trammel.Summary.All.11, Trammel.Summary.All.10, Trammel.Summary.All.9, Trammel.Summary.All.8,
   Trammel.Summary.All.7, Trammel.Summary.All.6, Trammel.Summary.FebDec.Year, 
   Trammel.Summary.FebDec.10.Year, Trammel.Summary.FebDec.9.Year, Trammel.Summary.FebDec.8.Year,
   Trammel.Summary.FebDec.7.Year, Trammel.Summary.FebDec.6.Year, Trammel.Summary.FebDec,
   Trammel.Summary.FebDec.10, Trammel.Summary.FebDec.9, Trammel.Summary.FebDec.8, 
   Trammel.Summary.FebDec.7, Trammel.Summary.FebDec.6, Trammel.Summary.MarDec.Year, 
   Trammel.Summary.MarDec.9.Year, Trammel.Summary.MarDec.8.Year, Trammel.Summary.MarDec.7.Year,
   Trammel.Summary.MarDec.6.Year, Trammel.Summary.MarDec, Trammel.Summary.MarDec.9, 
   Trammel.Summary.MarDec.8, Trammel.Summary.MarDec.7, Trammel.Summary.MarDec.6, 
   Trammel.Summary.MarNov.Year, Trammel.Summary.MarNov.8.Year, Trammel.Summary.MarNov.7.Year,
   Trammel.Summary.MarNov.6.Year, Trammel.Summary.MarNov, Trammel.Summary.MarNov.8, 
   Trammel.Summary.MarNov.7, Trammel.Summary.MarNov.6, Electro.Summary.All.11.Year, 
   Electro.Summary.All.10.Year, Electro.Summary.All.9.Year, Electro.Summary.All.8.Year, 
   Electro.Summary.All.7.Year, Electro.Summary.All.6.Year, Electro.Summary.All.11, 
   Electro.Summary.All.10, Electro.Summary.All.9, Electro.Summary.All.8, Electro.Summary.All.7, 
   Electro.Summary.All.6, Electro.Summary.FebDec.Year, Electro.Summary.FebDec.10.Year, 
   Electro.Summary.FebDec.9.Year, Electro.Summary.FebDec.8.Year, Electro.Summary.FebDec.7.Year, 
   Electro.Summary.FebDec.6.Year, Electro.Summary.FebDec, Electro.Summary.FebDec.10, 
   Electro.Summary.FebDec.9, Electro.Summary.FebDec.8, Electro.Summary.FebDec.7, 
   Electro.Summary.FebDec.6, Electro.Summary.MarDec.Year, Electro.Summary.MarDec.9.Year, 
   Electro.Summary.MarDec.8.Year, Electro.Summary.MarDec.7.Year, Electro.Summary.MarDec.6.Year, 
   Electro.Summary.MarDec, Electro.Summary.MarDec.9, Electro.Summary.MarDec.8, 
   Electro.Summary.MarDec.7, Electro.Summary.MarDec.6, Electro.Summary.MarNov.Year, 
   Electro.Summary.MarNov.8.Year, Electro.Summary.MarNov.7.Year, Electro.Summary.MarNov.6.Year, 
   Electro.Summary.MarNov, Electro.Summary.MarNov.8, Electro.Summary.MarNov.7, 
   Electro.Summary.MarNov.6, Trammel.Summary.Org, Electro.Summary.Org)
```

```{r}
save.image("Simulation Summaries.rdata")
```