---
title: "Simulation Plots"
author: "Joseph C. Ballenger, PhD"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: "hide"
    dev: "png"
    fig_height: 4.5
    fig_width: 6.5
    highllight: "tango"
    keep_md: TRUE
    smart: TRUE
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
    df_print: "paged"
  pdf_document:
    toc: TRUE
    toc_depth: 2
    fig.width: 13.33
    fig.height: 7.5
    fig.crop: TRUE
    dev: "png"
    df_print: "tibble"
    highlight: "tango"
    keep_tex: TRUE
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
# knitr options setting
knitr::opts_chunk$set(autodep = TRUE, fig.show = 'asis', fig.width = 13.33,
                      fig.height = 7.5, dev = "png", tidy = TRUE, 
                      dev.args = list(type = "windows", family = "serif"), 
                      dpi = 800, cache = TRUE, message = FALSE, echo = TRUE,
                      warning = FALSE)
# Number printing options
options(digits = 4)
# Required libraries
library(tidyverse)
library(FSA)
library(extrafont)
library(readxl)
library(survey)
```

```{r}
fig.width.powerpoint <- 13.33
fig.height.powerpoint <- 7.5
fig.width.word.l <- 6.5
fig.width.word.p <- 9
fig.height.word.l <- 3.5
fig.height.word.p <- 6

font.size.word <- 12
font.size.powerpoint <- 18
```

```{r}
load("Simulation Summaries.Rdata")
```

# Trammel net
## CPUE - Matplot
```{r, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Trammel.Combined$Species)) {
  tmp.org <- Trammel.Combined[Trammel.Combined$Species == species & 
                                Trammel.Combined$Month.SubSample == "Jan-Dec\n12 Months", ]
  tmp.sub <- Trammel.Combined[Trammel.Combined$Species == species, ]
  sample <- sample(tmp.sub$Run, 100, replace = FALSE)
  sample <- c(1, sample)
  tmp.sub <- tmp.sub[tmp.sub$R %in% sample, ]
  Subset.plot <- 
    ggplot(data = tmp.sub, 
           aes(x = as.numeric(as.character(Year)), y = Abundance)) +
    geom_line(aes(group = Run), alpha = 0.25) +
    facet_grid(rows = vars(Months), cols = vars(`Sub-Sampling`)) +
    annotate(geom = "ribbon",
             ymin = tmp.org$ci_l, ymax = tmp.org$ci_u, x = tmp.org$Year,
             alpha = 0.25, colour = NA, fill = "red") +
    annotate(geom = "line", y = tmp.org$Abundance, x = tmp.org$Year, color = "red") +
    labs(x = "Year", y = "Catch per Trammel Net",
         title = paste(species, "Relative Abundance")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"))
  ggsave(paste("Trammel Net/Plots/CPUE Matplot/", species,
               " CPUE - Original vs. Subsetting.png",
               sep = ""),
         device = "png",
         width = fig.width.powerpoint,
         height = fig.height.powerpoint,
         units = "in", dpi = 600)
  plot(Subset.plot)
}
```

## CPUE - Index Plot
```{r, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Trammel.CPUE$Species)) {
  tmp.org <- Trammel.CPUE[Trammel.CPUE$Species == species & 
                            Trammel.CPUE$Month.SubSample == "Jan-Dec\n12 Months", ]
  tmp.sub <- Trammel.CPUE[Trammel.CPUE$Species == species, ]
  Index.plot <-
    ggplot(data = tmp.sub) +
    geom_ribbon(aes(x = Year, ymin = ci_l, ymax = ci_u), fill = "black", alpha = 0.5) +
    geom_line(aes(x = Year, y = Abundance), color = "black") +
    facet_grid(rows = vars(Months), cols = vars(`Sub-Sampling`)) +
    annotate(geom = "ribbon", ymin = tmp.org$ci_l, ymax = tmp.org$ci_u, x = tmp.org$Year, 
             alpha = 0.5, colour = NA, fill = "red") +
    annotate(geom = "line", y = tmp.org$Abundance, x = tmp.org$Year, color = "red") +
    labs(x = "Year", y = "Catch per Trammel Net", 
         title = paste(species, "Relative Abundance")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"))
  ggsave(paste("Trammel Net/Plots/CPUE Index Plot/", species,
               " CPUE - Original vs. Subsetting Relative Abundance Index.png",
               sep = ""),
         device = "png",
         width = fig.width.powerpoint,
         height = fig.height.powerpoint,
         units = "in", dpi = 600)
  plot(Index.plot)
}
```

## Annual CV vs. Original CV
```{r, message = FALSE, error = FALSE, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
every_nth = function(n) {
  return(function(x) {x[c(TRUE, rep(FALSE, n - 1))]})
}
for(species in unique(Trammel.Combined$Species)) {
  tmp.org <- Trammel.Combined[Trammel.Combined$Species == species & 
                                Trammel.Combined$Month.SubSample == "Jan-Dec\n12 Months", ]
  tmp.sub <- Trammel.Combined[Trammel.Combined$Species == species, ]
  CV.plot <- ggplot(tmp.sub, aes(x = factor(Year), y = cv)) +
    geom_boxplot() +
    annotate(geom = "point", 
             x = factor(tmp.org$Year), 
             y = tmp.org$cv, 
             color = "blue") +
    labs(x = "Year", y = "Coefficient of Variation",
         title = paste(species, "Annual Coefficient of Variation")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"),
          axis.text.x = element_text(angle = 90, vjust = 0.4)) +
    facet_grid(rows = vars(Months), cols = vars(`Sub-Sampling`)) +
    scale_x_discrete(breaks = every_nth(n = 5), )
    
  ggsave(paste("Trammel Net/Plots/Annual CV by Species/", species, 
               " Annual CV - Original (Blue Dot) vs. Subsetting.png", 
               sep = ""),
         device = "png", 
         width = fig.width.powerpoint, 
         height = fig.height.powerpoint, 
         units = "in", dpi = 600)
  plot(CV.plot)
}
```

## Change in Median Annual CV by Species
### Change in CV
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Trammel.Summary$Species)) {
CV.plot <- ggplot(Trammel.Summary[Trammel.Summary$Species == species, ], 
                  aes(x = Month.SubSample, y = Median.CV, group = Month.SubSample)) +
  geom_point() +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = paste(species, "Median Coefficient of Variation")) +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.2))
ggsave(paste("Trammel Net/Plots/Median CV by Species/", species, 
             " CV - Overhaul Options.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
}
```

## Relative Change
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Trammel.Summary$Species)) {
CV.plot <- ggplot(Trammel.Summary[Trammel.Summary$Species == species, ], 
                  aes(x = Month.SubSample, y = Relative.CV, group = Month.SubSample)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Design Change", y = "Relative Change in CV",
       title = paste(species, "% Change in CV")) +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.2))
ggsave(paste("Trammel Net/Plots/Median CV by Species/", species, 
             " CV - Overhaul Options - Relative Change in CV.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
}
```

### Boxplots 
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Trammel.Combined$Species)) {
  df <- Trammel.Combined[Trammel.Combined$Species == species, ] %>%
    group_by(Species, Month.SubSample, Year) %>%
    summarize(cv = median(cv)) %>%
    ungroup()
  CV.plot <- ggplot(df, aes(x = Month.SubSample, y = cv)) +
    geom_boxplot() +
    labs(x = "Design Change", y = "Coefficient of Variation",
         title = paste(species, "Coefficient of Variation")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"),
          axis.text.x = element_text(angle = 90, vjust = 0.3))
  ggsave(paste("Trammel Net/Plots/Median CV by Species/", species, 
               " CV - Overhaul Options - Boxplots.png", 
               sep = ""),
         device = "png", 
         width = fig.width.powerpoint, 
         height = fig.height.powerpoint, 
         units = "in", dpi = 600)
  plot(CV.plot)
}
```

### CVs Across Species
#### Box Plot
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
CV.plot <- ggplot(Trammel.Combined %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup(), 
                  aes(x = Month.SubSample, y = cv)) +
  geom_boxplot() +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = "Coefficient of Variation") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Trammel Net/Plots/Median CV Species Combined/", "CV Across All Species - Boxplots.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```

#### Relative Change
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
CV.plot <- ggplot(Trammel.Combined %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    mutate(Relative.cv = (cv / first(cv) - 1) * 100),
                  aes(x = Month.SubSample, y = Relative.cv)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = "Relative Change in CV") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Trammel Net/Plots/Median CV Species Combined/", "CV Across All Species - Relative Change.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```



### CVs Across Recreationally Important Finfish
#### Box Plot
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
Trammel.SelectSpecies <- c("Red Drum", "Spotted Seatrout", "Spot", "Southern Flounder",
                           "Black Drum", "Atlantic Croaker", "Sheepshead", "Southern Kingfish",
                           "Bluefish")
CV.plot <- ggplot(Trammel.Combined[Trammel.Combined$Species %in% Trammel.SelectSpecies, ] %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup(), 
                  aes(x = Month.SubSample, y = cv)) +
  geom_boxplot() +
  labs(x = "Overhaul Strategy", y = "Coefficient of Variation",
       title = "Coefficient of Variation") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Trammel Net/Plots/Median CV Species Combined/", "CV Across Select Species - Boxplots.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```

#### Relative Change
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
CV.plot <- ggplot(Trammel.Combined[Trammel.Combined$Species %in% Trammel.SelectSpecies, ] %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    mutate(Relative.cv = (cv / first(cv) - 1) * 100),
                  aes(x = Month.SubSample, y = Relative.cv)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = "Relative Change in CV") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Trammel Net/Plots/Median CV Species Combined/", "CV Across Select Species - Relative Change.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```

# Electrofishing
## CPUE - Matplot
```{r, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Electro.Combined$Species)) {
  tmp.org <- Electro.Combined[Electro.Combined$Species == species & 
                                Electro.Combined$Month.SubSample == "Jan-Dec\n12 Months", ]
  tmp.sub <- Electro.Combined[Electro.Combined$Species == species, ]
  sample <- sample(tmp.sub$Run, 100, replace = FALSE)
  sample <- c(1, sample)
  tmp.sub <- tmp.sub[tmp.sub$R %in% sample, ]
  Subset.plot <- 
    ggplot(data = tmp.sub, 
           aes(x = as.numeric(as.character(Year)), y = Abundance)) +
    geom_line(aes(group = Run), alpha = 0.25) +
    facet_grid(rows = vars(Months), cols = vars(`Sub-Sampling`)) +
    annotate(geom = "ribbon",
             ymin = tmp.org$ci_l, ymax = tmp.org$ci_u, x = tmp.org$Year,
             alpha = 0.25, colour = NA, fill = "red") +
    annotate(geom = "line", y = tmp.org$Abundance, x = tmp.org$Year, color = "red") +
    labs(x = "Year", y = "Catch per Electrofishing",
         title = paste(species, "Relative Abundance")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"))
  ggsave(paste("Electrofishing/Plots/CPUE Matplot/", species,
               " CPUE - Original vs. Subsetting.png",
               sep = ""),
         device = "png",
         width = fig.width.powerpoint,
         height = fig.height.powerpoint,
         units = "in", dpi = 600)
  plot(Subset.plot)
}
```

## CPUE - Index Plot
```{r, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Electro.CPUE$Species)) {
  tmp.org <- Electro.CPUE[Electro.CPUE$Species == species & 
                            Electro.CPUE$Month.SubSample == "Jan-Dec\n12 Months", ]
  tmp.sub <- Electro.CPUE[Electro.CPUE$Species == species, ]
  Index.plot <-
    ggplot(data = tmp.sub) +
    geom_ribbon(aes(x = Year, ymin = ci_l, ymax = ci_u), fill = "black", alpha = 0.5) +
    geom_line(aes(x = Year, y = Abundance), color = "black") +
    facet_grid(rows = vars(Months), cols = vars(`Sub-Sampling`)) +
    annotate(geom = "ribbon", ymin = tmp.org$ci_l, ymax = tmp.org$ci_u, x = tmp.org$Year, 
             alpha = 0.5, colour = NA, fill = "red") +
    annotate(geom = "line", y = tmp.org$Abundance, x = tmp.org$Year, color = "red") +
    labs(x = "Year", y = "Catch per Electrofishing", 
         title = paste(species, "Relative Abundance")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"))
  ggsave(paste("Electrofishing/Plots/CPUE Index Plot/", species,
               " CPUE - Original vs. Subsetting Relative Abundance Index.png",
               sep = ""),
         device = "png",
         width = fig.width.powerpoint,
         height = fig.height.powerpoint,
         units = "in", dpi = 600)
  plot(Index.plot)
}
```

## Annual CV vs. Original CV
```{r, message = FALSE, error = FALSE, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Electro.Combined$Species)) {
  tmp.org <- Electro.Combined[Electro.Combined$Species == species & 
                                Electro.Combined$Month.SubSample == "Jan-Dec\n12 Months", ]
  tmp.sub <- Electro.Combined[Electro.Combined$Species == species, ]
  CV.plot <- ggplot(tmp.sub, aes(x = factor(Year), y = cv)) +
    geom_boxplot() +
    annotate(geom = "point", 
             x = factor(tmp.org$Year), 
             y = tmp.org$cv, 
             color = "blue") +
    labs(x = "Year", y = "Coefficient of Variation",
         title = paste(species, "Annual Coefficient of Variation")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"),
          axis.text.x = element_text(angle = 90, vjust = 0.4)) +
    facet_grid(rows = vars(Months), cols = vars(`Sub-Sampling`)) +
    scale_x_discrete(breaks = every_nth(n = 5), )
    
  ggsave(paste("Electrofishing/Plots/Annual CV by Species/", species, 
               " Annual CV - Original (Blue Dot) vs. Subsetting.png", 
               sep = ""),
         device = "png", 
         width = fig.width.powerpoint, 
         height = fig.height.powerpoint, 
         units = "in", dpi = 600)
  plot(CV.plot)
}
```

## Change in Median Annual CV by Species
### Change in CV
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Electro.Summary$Species)) {
CV.plot <- ggplot(Electro.Summary[Electro.Summary$Species == species, ], 
                  aes(x = Month.SubSample, y = Median.CV, group = Month.SubSample)) +
  geom_point() +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = paste(species, "Median Coefficient of Variation")) +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.2))
ggsave(paste("Electrofishing/Plots/Median CV by Species/", species, 
             " CV - Overhaul Options.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
}
```

## Relative Change
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Electro.Summary$Species)) {
CV.plot <- ggplot(Electro.Summary[Electro.Summary$Species == species, ], 
                  aes(x = Month.SubSample, y = Relative.CV, group = Month.SubSample)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Design Change", y = "Relative Change in CV",
       title = paste(species, "% Change in CV")) +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.2))
ggsave(paste("Electrofishing/Plots/Median CV by Species/", species, 
             " CV - Overhaul Options - Relative Change in CV.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
}
```

### Boxplots 
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
for(species in unique(Electro.Combined$Species)) {
  df <- Electro.Combined[Electro.Combined$Species == species, ] %>%
    group_by(Species, Month.SubSample, Year) %>%
    summarize(cv = median(cv)) %>%
    ungroup()
  CV.plot <- ggplot(df, aes(x = Month.SubSample, y = cv)) +
    geom_boxplot() +
    labs(x = "Design Change", y = "Coefficient of Variation",
         title = paste(species, "Coefficient of Variation")) +
    theme_bw() +
    theme(legend.position = "none",
          text = element_text(family = "Calibri", 
                              size = font.size.powerpoint, 
                              face = "bold"),
          axis.text.x = element_text(angle = 90, vjust = 0.3))
  ggsave(paste("Electrofishing/Plots/Median CV by Species/", species, 
               " CV - Overhaul Options - Boxplots.png", 
               sep = ""),
         device = "png", 
         width = fig.width.powerpoint, 
         height = fig.height.powerpoint, 
         units = "in", dpi = 600)
  plot(CV.plot)
}
```

### CVs Across Species
#### Box Plot
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
CV.plot <- ggplot(Electro.Combined %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup(), 
                  aes(x = Month.SubSample, y = cv)) +
  geom_boxplot() +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = "Coefficient of Variation") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Electrofishing/Plots/Median CV Species Combined/", "CV Across All Species - Boxplots.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```

#### Relative Change
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
CV.plot <- ggplot(Electro.Combined %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    mutate(Relative.cv = (cv / first(cv) - 1) * 100),
                  aes(x = Month.SubSample, y = Relative.cv)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = "Relative Change in CV") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Electrofishing/Plots/Median CV Species Combined/", "CV Across All Species - Relative Change.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```

### CVs Across Recreationally Important Finfish
#### Box Plot
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
Electro.SelectSpecies <- c("Red Drum", "American Eel", "Southern Flounder", "Atlantic Croaker",
                           "Spotted Seatrout", "Striped Bass")
CV.plot <- ggplot(Electro.Combined[Electro.Combined$Species %in% Electro.SelectSpecies, ] %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup(), 
                  aes(x = Month.SubSample, y = cv)) +
  geom_boxplot() +
  labs(x = "Overhaul Strategy", y = "Coefficient of Variation",
       title = "Coefficient of Variation") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Electrofishing/Plots/Median CV Species Combined/", "CV Across Select Species - Boxplots.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```

#### Relative Change
```{r, warning = FALSE, fig.width = fig.width.powerpoint, fig.height = fig.height.powerpoint}
CV.plot <- ggplot(Electro.Combined[Electro.Combined$Species %in% Electro.SelectSpecies, ] %>%
                    group_by(Species, Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample, Year) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    group_by(Month.SubSample) %>%
                    summarize(cv = median(cv, na.rm = TRUE)) %>%
                    ungroup() %>%
                    mutate(Relative.cv = (cv / first(cv) - 1) * 100),
                  aes(x = Month.SubSample, y = Relative.cv)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Design Change", y = "Coefficient of Variation",
       title = "Relative Change in CV") +
  theme_bw() +
  theme(legend.position = "none",
        text = element_text(family = "Calibri", 
                            size = font.size.powerpoint, 
                            face = "bold"),
        axis.text.x = element_text(angle = 90, vjust = 0.3))
ggsave(paste("Electrofishing/Plots/Median CV Species Combined/", "CV Across Select Species - Relative Change.png", 
             sep = ""),
       device = "png", 
       width = fig.width.powerpoint, 
       height = fig.height.powerpoint, 
       units = "in", dpi = 600)
plot(CV.plot)
```




